An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-24 paper/paper.tex
Paper: start Future Work

@@

% Incorporate security into the design of our system
% - DHT (add digital signatures to each column, have each updater sign over old data like in bitcoin's blockchain)

% NAT traversal of client

>>>>

% TODO digital signatures? discussed in future work

@@

\subsection{BTBackup Security} \label{subsec:BTBackupSecurity}

We would like to see our system design incorporate security. Specifically, the DHT should have some scheme that ensures (1) entries cannot be tampered with by the node responsible for them and (2) nodes cannot lie about the data with which they are involved. We believe both of these goals can be achieved through the use of chained digital signatures.

Regarding (1), there could be a digital signature encompassing the entire entry to prevent the responsible node from modifying it. Perhaps the node that the entry describes could digitally sign it upon modification; or maybe the most recent node to modify an entry could digitally sign it. These solutions solve the immediate problem, but bring about additional ones that need to be investigated.

An example solution for (2): the communication between peers during the "Finding Replication Nodes" phase of backing up a file could be extended to require both parties digitally sign the information. That is, when a peer informs a node it will be backing up a given file of a given size, the DHT can store an additional entry containing their digital signatures, binding them to the exchange. This provides non-repudiation for the amount of data a peer is backing up and a node is storing, each of which a malicious user is incentivized to lie about. This solution does not deal with the blacklisters data, though a similar scheme for that is easy to imagine.

To reduce the size of the DHT with the addition of these digital signatures, a chaining mechanism could be put in place, similar to the one in Bitcoin's blockchain. Instead of appending digital signatures to the corresponding DHT column, new digital signatures could sign the old ones and then overwrite them. This preserves their effect, but removes the associated storage cost. More thought needs to be given to this to design an optimal mechanism (and to determine if chaining is even required).

\subsection{NAT Traversal}

As it stands now, our system is unusable by a majority of Internet users, since they live behind routers with NAT. We need to implement some mechanism to bypass this. We can turn to Skype, BitTorrent, BitTorrent Sync, and other P2P applications for inspiration.

\subsection{BTBackup Implementation}

There are many features missing from our implementation that we would like to see added. A brief, nonexhaustive list follows. It do not include features also missing from the specification.

\begin{enumerate}
    \item Replace the centralized tracker with a DHT
    \item Encrypted communication between peers to reduce information leakage
    \item The ability to backup folders, not just files
\end{enumerate}

% TODO there are more things missing from impl

% TODO there are more things missing from spec
